First and foremost, I would like to express my deepest gratitude to my advisor Prof. Liang Qi for his continuous guidance of my study, great patience, and immense knowledge. It is my honor to be the first student to join his research group. I am grateful for the open and inclusive collaboration culture he created across the group. I am fortunate to have Prof. Qi not only as a good mentor in academic research but also as a good mentor in my life. Prof. Qi inspired me with his enthusiasm for science. The problem-solving skills and attitude to others which I learned from him will guide me, no matter what I do in the future. I sincerely appreciate all he has done for me.

Besides, I would like to express my sincere thanks to Prof. Amit Misra, Prof. Emmanouil Kioupakis, and Prof. Fei Gao for serving on my thesis committee. The path to a Ph.D. is long, rocky and confusing. Without their insightful suggestions, unlimited help, and generous encouragement, I could not have gone that far.

I also would like to thank my group mates: Chaoming Yang, Dr. Yong-Jie Hu, Aditya Sundar, Zhucong Xi, and Bin Bin for your help, your support, and many memorable moments. You guys are the best! I would like to thank other colleagues from U-M: Nocona Sanders, Dr. Erica Chen, and Dr. Cheng Zhang for their collaboration and discussion. I am also grateful to the MSE Department for all the support. I also want to thank Dr. Louis Hector, Jr., Prof. L. Jay Guo, Dr. Jing-Yu Lao for their great collaboration. 

I am also grateful and feel lucky for funding supports provided by Materials Science and Engineering Department, Guardian Industry, General Motors, and National Science Foundation Grant Opportunities for Academic Liaison with Industry (GOALI) program. I thank computational resources provided by the University of Michigan HPC Great Lakes, Extreme Science and Engineering Discovery Environment (XSEDE),  National Energy Research Scientific Computing Center (NERSC).

I would like to thank my dearest friends: Ruiming Lu, Dandan Wang, Patrick (Peng) Sun, and Judy (Xin-Yi) Song.

At last, I would like to thank my family. I would like to thank my parents for their support, understanding, and love. And I would like to thank my beautiful wife Yan Zhang for her love, company, and tolerance. I love you all.