In this chapter, we focuses on the methodology development on simulating the solute clustering kinetics in multicomponent Al alloys quantitatively. To slow down solute clustering at room temperatures (so-called natural aging) after the high-temperature solid-solution treatment is crucial to expand the time window for the mechanical forming of certain high-strength multicomponent Al alloys, such as 7000 series Al-Mg-Zn alloys. Since the clustering is achieved by solute diffusion based on vacancy migration, we first discuss the relationship between vacancy migration barriers and local lattice occupation environments. It is found that the traditional bond counting method fails to predict vacancy migration barriers for the multicomponent systems. Second, a \acf{NN} surrogate model based on the first-principle training data set is introduced to predict the vacancy migration barrier accurately. Third, a \acf{kMC} simulation package based on \ac{NN} model with advanced acceleration methods, such as parallel schema, \acf{LRU} cache, \acf{LSKMC} is introduced to simulate the solute clustering kinetics in multicomponent Al alloys. Last but not least, the visualization and characterization methods of solute clusters in the kMC simulation results are investigated. The information on cluster compositions and structures lays the foundation for the studies of the clustering effects on the strengths and formability of multicomponent Al alloys in the future.

\input{Chap5/Introduction}
\input{Chap5/Fitting}
\input{Chap5/KMC}
\input{Chap5/Results}
\input{Chap5/Conclusion}