In this chapter, the thermodynamic driving force of H adsorption on anion-terminated (000$\overline{1}$) surfaces of pure and doped wurtzite ZnO, which is the dielectric substrate for Ag thin film deposition by sputtering, are investigated under varying H surface coverage conditions. A $\frac{1}{2}$ \ac{ML} of adsorbed H changes the electronic structure of pure ZnO (000$\overline{1}$) surface from metallic to semiconductor state by saturating unpaired electrons of surface oxygen atoms. This closed-shell electron configuration of ZnO (000$\overline{1}$) surface significantly reduces the adsorption strengths of subsequent H atoms, making the dissociative adsorption of a hydrogen molecule endothermic. A simple electron counting model is applied to predict and tune the coverage-dependent H adsorption strengths on doped ZnO surfaces. The equilibrium H coverage, above which the dissociative adsorption of a hydrogen molecule is endothermic, will decrease when doping elements (such as Al, Ti, and V) have more valence electrons than Zn. We also expand the method of tuning H equilibrium coverage to other similar polar semiconductors, such as wurtzite GaN (000$\overline{1}$), and zincblende ZnS ($\overline{1}$$\overline{1}$$\overline{1}$) surfaces. This method provides a general way to generate desired surface configurations of dielectric substrates before sputtering. The results will be used in the following chapter, Chapter \ref{chap:Ag/ZnO}, where multiscale simulation efforts are made to improving the Ag thin-film quality during sputtering by changing substrate structures and chemistry.

\input{Chap1/Introduction}
\input{Chap1/Coverage-dependent}
\input{Chap1/Electronic}
\input{Chap1/Dopants}
\input{Chap1/Generalization}
\input{Chap1/Conclusions}