% Metal/oxide interfaces are among the most important heterogeneous structures because various thin films are present in optical coatings, semiconductor devices, and catalysts. Therefore it is important to understand the thin film stability and morphology evolution during deposition processes. From this study, we will understand: (1) What are the major factors that affect metal thin film morphology during the deposition? (2) How do we improve the wettability of metallic thin films on the oxide substrates?

% To answer these two questions, \ac{GCMC} simulations are conducted on various substrates based on Ag-substrate bonding strength obtained from H-saturated ZnO (000$\overline{1}$) surfaces, with different lattice constants and substrate orientations. Among these parameters, substrate orientation is critical to Ag thin film quality. It turns out that the hexagonal substrate is robust for Ag thin film growth under different lattice constants and yields the best Ag thin film quality with \{111\} orientation because misfit dislocations are easier to generate hence helping interface stress released. By adding a trace amount of ``anchor'' sites on the substrate, thin-film morphology becomes much smoother and more continuous. Then high throughput \ac{DFT} calculations are used to identify potential ``anchor'' elements. Five elements, Pd, Sb, Se, Sn, and Te, are found to have the ability to act as ``anchor'' site elements that can increase Ag nucleation densities on substrates that have weak bonding to metallic thin films. Besides, we will also investigate alloy segregation on Ag grain boundaries to stabilize Ag thin films during heat treatment.

In this chapter, we utilize \acf{GCMC} simulation to understand the possible reason why ZnO is the appropriate substrate for Ag thin film deposition. The quality of Ag thin film on the hexagonal surfaces of the substrate, like ZnO (000$\overline{1}$), is robust to the variations of the substrate lattice constant and the Ag adsorption strength. \ac{GCMC} simulations on these hexagonal surfaces usually yield Ag thin films that are in the fcc phase and \{111\} orientated. Besides, to achieve more continuous Ag thin films with less use of Ag, the doping elements, like Pd, Sb, Se, Sn, and Te, can be added as ``anchor'' sites on ZnO surfaces to bind incoming Ag atoms. With 0.05\ac{ML} of ``anchor'' sites on the substrate, sufficient nuclei can be generated to achieve continuous ultra-thin films. We also search for alloying elements that can segregate in Ag grain boundaries to stabilize grain size during heat treatments. Current \ac{DFT} calculation shows that tungsten (W) does not segregate to any investigated Ag grain boundaries. This result is inconsistent with the experimental fact that W can stabilize Ag grain boundaries during the heat treatment. The possible origin of such inconsistency can be resolved if more accurate and representative grain boundary structures in Ag alloys are constructed in future studies.

\input{Chap4/Introduction}
\input{Chap4/Customized}
\input{Chap4/ZnO_substrate}
\input{Chap4/Anchor}
\input{Chap4/GB}
\input{Chap4/Conclusions}